Recreating NYT election map

### 2021-03-16 _post/2020-06-08-update-on-mobility-patterns/update-on-mobility-patterns.Rmd
post authorship

author:
  - first_name: "Roland"
    last_name: "Schmidt"
    url: https://werk.statt.codes
    orcid_id: 0000-0002-6897-1693
categories:
  - Austria
  - climate
  - Corona virus
  - shiny

>>>>

author:
  - first_name: "Roland"
    last_name: "Schmidt"
    url: https://werk.statt.codes
    orcid_id: 0000-0002-6897-1693
categories:
  - Austria
  - climate
  - COVID
  - shiny

### 2021-03-16 _post/2020-11-18-recreating-nyt-election-map/recreating-nyt-election-map.Rmd
post authorship

author:
  - first_name: "Roland"
    last_name: "Schmidt"
    url: https://werk.statt.codes
    orcid_id: 0000-0002-6897-1693
categories:
  - Austria
  - Corona virus
  - OCR
  - stringr
  - web scraping

>>>>

author:
  - first_name: "Roland"
    last_name: "Schmidt"
    url: https://werk.statt.codes
    orcid_id: 0000-0002-6897-1693
categories:
  - Austria
  - COVID
  - OCR
  - stringr
  - web scraping
